\documentclass{article}

\begin{document}

\begingroup
  \centering
  \textbf{\Large Welcome to the \confYear\ CCSC \confName\ Conference\par}
\endgroup

\vspace{10pt}

The 2019 South Central Steering Committee is very pleased to welcome everyone
to our 30th annual conference in Richardson, Texas hosted by the University of
Texas at Dallas.  Our conference chair and host, Sam Karrah, has provided
wonderful facilities for the conference and the support of his department and
staff has been outstanding.  Several faculty and staff at the University of
Texas at Dallas have given extensive time and generous efforts to our conference
and committee throughout this past year.  Their efforts and congeniality are
very much appreciated.

This year we have eight papers, two workshops, several lightning talks, and
both student and faculty posters on the program.  The Steering Committee chose
8 of 14 papers through a double-blind review process for a paper acceptance rate
of 57\%.  We had 21 colleagues across the region and country serve as
professional reviewers and we recognize their generous efforts in providing
time and guidance in the selection of our conference program.

The Steering Committee invites colleagues to host the conference in the future
and to join our community of computer science educators to enrich our curricula
and provide innovative pedagogy for our students. We encourage other members of
the South Central region to attend our Friday evening business meeting and to
join in our efforts to bring in fellow colleagues who wish to be involved in
the planning and execution of the conference in the future.

We extend a very warm and delightful welcome to all presenters and attendees
and encourage everyone to enjoy our program and the University of Texas at
Dallas.  Thank you again to all members of the 2019 Steering Committee who
continue to provide the necessary time and dedication to the conference with
grace and cherished commitment.

\vspace{10pt}

\hfill Sam Karrah

\hfill University of Texas at Dallas

\hfill Conference Chair and Host

\vspace{10pt}

\hfill Laura J. Baker

\hfill St. Edward's University

\hfill Papers and Program Chair

\end{document}
